\documentclass{piotrcv}
\usepackage[english]{babel}
\usepackage{mathtools}
\usepackage{relsize}
\begin{document}
\setlength{\emergencystretch}{3em}
\part{Piotr Kurkiewicz}

\section{Projects}

%\newcommand{printfriendly}

\newcommand{\specialname}{Why HP?}
\newcommand{\specialcontents}{I am a great fan of economy and business, but I have my favourite way, which I like business to be done. Unusually for a large company HP does the business in a way which coincides with my beloved start-up-like work culture: the HP-way. The fact that the company founders have set it up in a garage must have had a major influence on how they treated their workers -- who overall are similar human-beings, a thing many big players on the market would often forget about. \medskip\newline 
I believe in the company’s sustainable way of managing their resources. Sustainability is exceptionally important in modern days, and technology has proven many times to be one of our strongest hopes in that field. I would like to be a part of a community which is both economically and environmentally aware and active.
Finally I would be honoured to work in Bucharest, a city which has played a major historical role in Eastern Europe, and nowadays a place of vast economic growth and technological development.}

\begin{eventlist}

\item{Collaboration with Ceneo.pl}
     {Investigation of factors motivating consumers to submit a post-purchase review}
     {In my second year as a member of Economic Analysis Society I have taken part in a joint project with Ceneo.pl, a leading Polish price comparator, an e-commerce hiring 120 people and an engaged member of business community in Wroclaw. The goal of the project has been to understand and expose factors that influence consumers to submit an opinion about their purchase. Within the team my responsibility was in application of techniques from Qualitative Analysis and Focus Group Interview. I have also participated in deployment of a survey to the main website of the company gathering 2000 responses over 2 days. Dataset we have gathered has been analysed with deep scrutiny and our results have made a real difference to the company.}
     {ceneo.pl}

\item{Econometrics}
     {Building a statistical model of Polish GDP growth}
     {In this University assignment carried out in pair with my classmate I have designed and statistically tested a model of Polish GDP growth as predicted by 2 factors: import of foreign goods and number of university graduates per annum. In the process I had to use advanced features of Excel\textregistered\ spreadsheet and show excellent understanding of underlying statistics, rejecting the null hypotheses and eliminating factors, which we found statistically insignificant. Our work has achieved a top mark and as the time passed by we had personal satisfaction to discover that our prediction has been highly accurate.}
     {github.com/picrin/VAIDA}

\item{Operations research}
     {Optimal decision making in enterprise planning}
     {In this individual project I had to make a creative use of Excel\textregistered\ macros in order to analyse a task dependency graph looking for the most efficient way of organising a large event. Carrying out the task I enjoyed putting my creativity into a rigid framework of mathematical reasoning and I have strengthened my Excel\textregistered\ skills and developed basic programming skills.}
     {github.com/picrin/StockExchange}

\end{eventlist}

\personal
    []
    {Pl. Oddz. Mlodz. Powst 4/8 \newline 40 061 Katowice, Poland}
    {+48 516 215 333}
    {kurkiewiczpiotr@gmail.com}

\section{Education}

\begin{yearlist}


\item[Wroclaw University of Economics]
     {2012 - 2017}
     {Economic Analytics with Business Decision Analytics}
     {Wroclaw, Poland}

\item[FOSA Security]
     {2011 - Now\ }
     {security guard}
     {South-West Poland}

\item[III Adam Mickiewicz HS]
     {2009 - 2012}
     {Polish Matura}
     {Katowice, Poland}



\end{yearlist}

\section{Personal Skills}

\begin{skillist}
\item{Organiser} {In December 2013 I have co-organized the Academy of Talents -- a competition which has engaged over 120 students and a dozen of most influential Wroclaw entrepreneurs, managers and decision-makers. During a three stage processes the jury has chosen 10 best participants, all of whom have been awarded 3-month internships shadowing crucial positions in the industry and the public sector.}
\item{Team player} {Over the course of my degree I have been engaged in a number of student business organisations such as Business Competencies Forum, where I have constantly cooperated with some of the most enthusiastic and creative people, students, university researchers and businessmen alike to give my alma mater a vibrant platform of economic thought exchange by organising competitions and inspiring lectures. I have always embraced teamwork, and I know that true greatness can be only achieved together.}
\item{Professional Responsibility} {Since graduation from High School I have worked part-time as a security guard at musical concerts throughout South-West Poland as an on-call employee of \textit{Fosa}, a safe guarding company. As English fluency in the company is not common among workers, I would be often assigned to direct protection of foreign performers, such as Rihanna, Coldplay, Madonna and other famous pop-stars. This type of work has taught me to faithfully carry out my professional duties in some of the most demanding, often dangerous situations. This job has given me incredible confidence and prepared me for many challenges in my future career.}
\item{Broad Horizons}{My interests are not limited to Economics and Business. As a sport lover I spend a few hours every second day hiking, climbing, running, rowing or simply body-building in one of many University's sports facilities. I had been a dedicated Rugby player until I had to stop due to medical reasons. I like new technologies and gaming. Among my friends I am recognised as a strong Warcraft III player. I have travelled to most European countries, often hitch-hiking, which has helped me to build excellent relations with all sorts of people from all sorts of background.}
\end{skillist}

\newpage

\section{\specialname}
\specialcontents

\end{document}
